Forschungsprojekt

### 2020-10-13 documentation/presentation/main.tex
:-)

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{biblatex}
\usepackage{tikz}
\usetikzlibrary{positioning}

\setlength{\parskip}{0pt}
\raggedcolumns

\bibliography{bib.bib}

@@

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

We compare some state-of-the-art non-uniform memory access (NUMA) aware systems and Giraph in terms of performance, both on real world and synthetic graphs.
Therefore, we evaluate the three algorithms Single-Source Shortest-Paths (SSSP), Breadth-First Search (BFS) and PageRank (PR).
We compare not only the time the frameworks indicate, they need to compute, but also the time they actually run and consume resources, as well as the resulting overhead time.

@@

	\subsection{Algorithms}
	\begin{description}
		\item[Single-Source Shortest-Paths (SSSP):] find the shortest path from a starting vertex to every other vertex

@@

\clearpage
\section{Hugepages}

\clearpage
\section{Frameworks}

\clearpage
\section{Evaluation}
\begin{multicols}{2}
\noindent 5 Machines, with
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each, one machine only 128 GB
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.)
\end{itemize}

\renewcommand{\arraystretch}{1.2}%
{%
\noindent
\centering
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
}%

@@

Messfehlern bei Galois Calc was sagen

\clearpage
\section{Production Case Single Node}

@@

\clearpage
\section{Production Case Distributed}

@@

\clearpage
\section{Research Case Distributed}

@@

\section{Conclusion and Outlook}
Für jeden Fall ist das beste Framework sehr spezifisch.
Blabla.

Outlook:
Immer wieder solche Tests machen, viele der Frameworks ändern sich immer wieder weiter und so, nicht wahr.

\clearpage
\nocite{unserPaper}
\printbibliography
\end{document}

>>>>

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{tikz}
\usetikzlibrary{positioning}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{1cm}
\raggedcolumns

@@

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
\begin{itemize}
	\item 
In the past years several graph processing systems emerged.
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.
\item Comparison of non-uniform memory access (NUMA) aware systems and Giraph in their performance
\begin{itemize}
	\item on different graphs (real world and synthetic)
\item and different algorithms (SSSP, BFS, PR)
\end{itemize}
\end{itemize}

@@

	\subsection*{Algorithms}
	\begin{description}
		\item[Single-Source Shortest-Paths (SSSP):] find the shortest path from a starting vertex to every other vertex

@@

\section{Hugepages}

\section{Frameworks}

\definecolor{Galois}{HTML}{1f77b4}
\definecolor{Gemini}{HTML}{ff7f0e}
\definecolor{Giraph}{HTML}{2ca02c}
\definecolor{Ligra}{HTML}{d62728}
\definecolor{Polymer}{HTML}{9467bd}

\begin{multicols}{2}
\begin{description}
	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
	\begin{itemize}
		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
	\end{itemize}
	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
	\begin{itemize}
		\item Version from 2\textsuperscript{nd} November 2016 used
		\item Version contains bugs that had to be fixed 
	\end{itemize}
	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
	\begin{itemize}
		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
		\item BFS is not natively supported 
	\end{itemize}
	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
	\begin{itemize}
		\item Version from 14\textsuperscript{th} August 2019
	\end{itemize}
	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
	\begin{itemize}
		\item Version from 28\textsuperscript{th} August 2018
	\end{itemize}
\end{description}
\end{multicols}

\section{Evaluation}
\begin{multicols}{2}
\noindent 5 Machines, with
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each, one machine only 128 GB
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.)
\end{itemize}

\begin{center}
	\renewcommand{\arraystretch}{1.2}%
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
\end{center}

@@

\section{Production Case Single Node}

@@

\section{Production Case Distributed}

@@

\section{Research Case Distributed}

@@

\section{Galois With Hugepages}
\begin{multicols}{2}

\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5 \\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1 \\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1 \\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4 \\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5 \\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1 \\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6 \\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4 \\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3 \\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1 \\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1 \\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4 \\
		\bottomrule
\end{tabular}

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	SSSP

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
	PR Pull
\end{multicols}

\section{Conclusion and Outlook}
\begin{itemize}
	\item performance highly dependent on the framework, algorithm and data set
	\begin{itemize}
		\item Galois is almost always fastest in the research case; especially with hugepages
		\item Giraph is good on SSSP or BFS in distributed production
		\item Gemini is a good middleground for distributed PR and single node production
	\end{itemize}

	\item single node almost always preferrable, as long as RAM is sufficient
\end{itemize}

\subsection{Outlook}
\begin{itemize}
	\item[$\rightarrow$] incorporate new frameworks and new algorithms
	\item[$\rightarrow$] great range of settings and multiple implementations for the same problem
	\item[$\rightarrow$] At a later point in time, it is important to repeat such a comparison, because the frameworks are further developed and new ones are created.
\end{itemize}

\end{document}
